Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-06-05 paper/paper.tex
upload violin and flute figures

\usepackage{amsthm,amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{color}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{musicography}
\usepackage{relsize}
\usepackage{siunitx}
% \def\includegraphic[#1]{}
% \def\includegraphics[#1]{}

@@

\begin{figure}
\caption{\csentence{Sample scattering}
Same 3 sounds spectrogram + scattering
% TODO figure + caption
}
\label{fig:sample-scattering}
\end{figure}

>>>>

\usepackage{amsthm,amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{color}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{musicography}
\usepackage{pdfpages}
\usepackage{relsize}
\usepackage{siunitx}
% \def\includegraphic[#1]{}
% \def\includegraphics[#1]{}

@@

\begin{figure}
\includegraphics[width=0.23\textwidth]{figures/violin_scattering/Vn-ord-C4-mf-4c_scalogram.pdf}
\includegraphics[width=0.23\textwidth]{figures/violin_scattering/Vn-tasto-C4-mf-4c_scalogram.pdf}
\includegraphics[width=0.23\textwidth]{figures/violin_scattering/Vn-trem-C4-mf-4c_scalogram.pdf}
\includegraphics[width=0.23\textwidth]{figures/violin_scattering/Vn-stacc-C4-mf_scalogram.pdf}

\includegraphics[width=0.23\textwidth]{figures/violin_scattering/Vn-ord-C4-mf-4c_scattering-compressed.pdf}
\includegraphics[width=0.23\textwidth]{figures/violin_scattering/Vn-tasto-C4-mf-4c_scattering-compressed.pdf}
\includegraphics[width=0.23\textwidth]{figures/violin_scattering/Vn-trem-C4-mf-4c_scattering-compressed.pdf}
\includegraphics[width=0.23\textwidth]{figures/violin_scattering/Vn-stacc-C4-mf_scattering-compressed.pdf}
\caption{\csentence{Violin scattering}}
\label{fig:violin-scattering}
\end{figure}

\begin{figure}
\includegraphics[width=0.23\textwidth]{figures/flute_scattering/Fl-ord-C4-mf_scalogram.pdf}
\includegraphics[width=0.23\textwidth]{figures/flute_scattering/Fl-sfz-C4-fp_scalogram.pdf}
\includegraphics[width=0.23\textwidth]{figures/flute_scattering/Fl-trill-maj2-C4-mf_scalogram.pdf}
\includegraphics[width=0.23\textwidth]{figures/flute_scattering/Fl-key-cl-C4-f_scalogram.pdf}

\includegraphics[width=0.23\textwidth]{figures/flute_scattering/Fl-ord-C4-mf_scattering_compressed.pdf}
\includegraphics[width=0.23\textwidth]{figures/flute_scattering/Fl-sfz-C4-fp_scattering_compressed.pdf}
\includegraphics[width=0.23\textwidth]{figures/flute_scattering/Fl-trill-maj2-C4-mf_scattering_compressed.pdf}
\includegraphics[width=0.23\textwidth]{figures/flute_scattering/Fl-key-cl-C4-f_scattering_compressed.pdf}
\caption{\csentence{Flute scattering}}
\label{fig:flute-scattering}
\end{figure}

\begin{figure}
\includegraphics[width=0.3\textwidth]{figures/violin_scattering/Vn-ord-C4-mf-4c_scalogram.pdf}
\includegraphics[width=0.3\textwidth]{figures/violin_scattering/Vn-tasto-C4-mf-4c_scalogram.pdf}
\includegraphics[width=0.3\textwidth]{figures/violin_scattering/Vn-trem-C4-mf-4c_scalogram.pdf}

\hspace{0.05\textwidth}
\includegraphics[width=0.25\textwidth]{figures/violin_scattering/Vn-ord-C4-mf-4c_scattering-compressed.pdf}
\hspace{0.05\textwidth}
\includegraphics[width=0.25\textwidth]{figures/violin_scattering/Vn-tasto-C4-mf-4c_scattering-compressed.pdf}
\hspace{0.05\textwidth}
\includegraphics[width=0.25\textwidth]{figures/violin_scattering/Vn-trem-C4-mf-4c_scattering-compressed.pdf}

\vspace{1cm}

\includegraphics[width=0.3\textwidth]{figures/violin_scattering/Vn-stacc-C4-mf_scalogram.pdf}
\includegraphics[width=0.3\textwidth]{figures/violin_scattering/Vn-nonvib-C4-mf-4c_scalogram.pdf}
\includegraphics[width=0.3\textwidth]{figures/violin_scattering/Vn-sfz-C4-fp-4c_scalogram.pdf}

\hspace{0.05\textwidth}
\includegraphics[width=0.25\textwidth]{figures/violin_scattering/Vn-stacc-C4-mf_scattering-compressed.pdf}
\hspace{0.05\textwidth}
\includegraphics[width=0.25\textwidth]{figures/violin_scattering/Vn-nonvib-C4-mf-4c_scattering-compressed.pdf}
\hspace{0.05\textwidth}
\includegraphics[width=0.25\textwidth]{figures/violin_scattering/Vn-sfz-C4-fp-4c_scattering-compressed.pdf}

\caption{\csentence{Violin scattering}}
\label{fig:violin-scattering}
\end{figure}
